Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2021-06-08 ms/Thesis/thesis.tex
Address other games such as Stag hunt in the model description

Not all adults become parents, and we denote the frequency of phenotype $A$ among parents by $\dot{p}$.
Therefore, the frequency $\hat{p}$ of  phenotype $A$ among juveniles (after selection and vertical and oblique transmission) is
\begin{equation}\label{eq:horizontal}
\begin{aligned}
\hat{p} \;=
\dot{p} [v + (1-v)p] + (1-\dot{p}) [(1-v)p] \;= 
v \dot{p} + (1-v) p \;.
\end{aligned}
\end{equation}
Individuals are assumed to interact according to a \emph{prisoner's dilemma}.
Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $c<b$. \autoref{fig:illustration}a shows the payoff matrix, i.e. the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$.

>>>>

Not all adults become parents, and we denote the frequency of phenotype $A$ among parents by $\dot{p}$.
Therefore, the frequency $\hat{p}$ of  phenotype $A$ among juveniles (after selection and vertical and oblique transmission) is
\begin{equation}\label{eq:horizontal}
\begin{aligned}
\hat{p} \;=
\dot{p} [v + (1-v)p] + (1-\dot{p}) [(1-v)p] \;= 
v \dot{p} + (1-v) p \;.
\end{aligned}
\end{equation}
Individuals are assumed to interact according to a \emph{prisoner's dilemma}.
Specifically, individuals interact in pairs; a cooperator suffers a fitness cost $0<c<1$, and its partner gains a fitness benefit $b$, where we assume $c<b$. \autoref{fig:illustration}a shows the payoff matrix, i.e. the fitness of an individual with phenotype $\phi_1$ when interacting with a partner of phenotype $\phi_2$.
The choise of prisoner's dilemma as the interaction model was motividated by the fact that prisoner's dilemma is a common game used to study evolution of cooperation\citep{axelrod1981evolution}, \citep{milinski1987tit}, \citep{nowak1992tit}.
Although we decided to focus on prisoner's dilemma, other games such as stag hunt\citep{skyrms2004stag} may be a better explaination of cooperation behavior in humman\citep{tomasello2012two}.
